Landau quantization of nearly degenerate bands, \\ and full symmetry classification of Landau-level crossings

### 2019-05-16 paper.tex
Updates from Overleaf

In the absence of symmetry,  it is well known (as the non-crossing rule in quantum theory\cite{neumann2000behaviour}) that eigenvalue-degeneracies of complex, finite-dimensional matrix Hamiltonians are attainable by tuning three parameters. Here and henceforth,   \textit{parameters}  will always refer to real parameters. Since unitary matrices are exponentiated Hamiltonians (multiplied by $i$), the eigenvalue-degeneracies of the two-by-two unitary propagator $\A$ [cf. \q{eq:prop}] are also attainable by tuning three parameters (in the absence of symmetry).\textbf{[Fritz Haake, chaos]} We briefly review how this  result is attained; the elementary argument that will be presented here will be nontrivially generalized to other symmetry classes of orbits in the subsequent sections.

>>>>

In the absence of symmetry,  it is well known (as the non-crossing rule in quantum theory\cite{neumann2000behaviour}) that eigenvalue-degeneracies of complex, finite-dimensional matrix Hamiltonians are attainable by tuning three parameters. Here and henceforth,   \textit{parameters}  will always refer to real parameters. Since unitary matrices are exponentiated Hamiltonians (multiplied by $i$), the eigenvalue-degeneracies of the two-by-two unitary propagator $\A$ [cf. \q{eq:prop}] are also attainable by tuning three parameters (in the absence of symmetry)\cite{haake2010quantum}. We briefly review how this  result is attained; the elementary argument that will be presented here will be nontrivially generalized to other symmetry classes of orbits in the subsequent sections.
